### 2022-11-27 ms.rmd
Adding in change on the converted q10 scale though

>>>>

# But this is the % change on the log scale. We can also see what the Q10 change is..NEED TO BE CHECKED CAREFULLY
f_q10 <-exp((f_acclim - f_acute)-1); mean(f_q10); quantile(f_q10, c(0.025, 0.975))
m_q10 <-exp((m_acclim - m_acute)-1); mean(m_q10); quantile(m_q10, c(0.025, 0.975))
t_q10 <-exp((t_acclim - t_acute)-1); mean(t_q10); quantile(t_q10, c(0.025, 0.975))
